---
title: "Alt Right Project"
output: github_document
---

```{r echo=F}
altright <- tibble::tribble(
            ~Content,          ~Link, ~Platform,
                    "Partly cloudy.",         "Brisbane",   19L,
                    "Partly cloudy.", "Brisbane Airport",   18L,
                  "Possible shower.",       "Beaudesert",   15L,
                    "Partly cloudy.",        "Chermside",   17L,
    "Shower or two. Possible storm.",           "Gatton",   15L,
                  "Possible shower.",          "Ipswich",   15L,
                    "Partly cloudy.",    "Logan Central",   18L,
                     "Mostly sunny.",            "Manly",   20L,
                    "Partly cloudy.",    "Mount Gravatt",   17L,
                  "Possible shower.",            "Oxley",   17L,
                    "Partly cloudy.",        "Redcliffe",   19L
    )

knitr::kable(altright)
```

# To Do 


- Flüge buchen
- Research Papers/Books
- Paper schreiben
- Neuen Korpus für Alt Right
- Include Alt Lite Figures!
-- Codewords erstellen 
-- Narratives
--- white people are marginalized
--- anti-feminism
--- Muslim invasion
--- "dysgenics/race-mixing/low IQ""
--- white ethnostate
- Hatefulness measuren
- Predictions # WHICH MEASURES?
- Sentiment Analysis
- Qualitative Robustness Check?
- Nazi Data/ Labelled Online Harassment data

# Interesting Links:

**A Longitudinal Measurement Study of 4chanâs Politically Incorrect Forum and its Effect on the Web**

http://absintt.be/app/uploads/2017/01/1610.03452v1.pdf

**Gamergate**

https://medium.com/message/72-hours-of-gamergate-e00513f7cf5d

**Alt-Lite Wiki**

https://en.wikipedia.org/wiki/Alt-lite

**Alt-Right Wiki**

https://en.wikipedia.org/wiki/Alt-right

**Media Manipulation And Disinformation Online**

https://datasociety.net/pubs/oh/DataAndSociety_MediaManipulationAndDisinformationOnline.pdf

**Alt-Right Open Intelligence Initiative**

*Mapping the Alt-Right: The US Alternative Right across the Atlantic*

https://wiki.digitalmethods.net/Dmi/AltRightOpenIntelligenceInitiative

** Alt Right You Tubers **

https://docs.google.com/document/d/1bi4q4W04NEYWFDRoL8VPJ-IqAvHxXkf-bdl-WG9IHWw/edit

**A Network Analysis of White Nationalism: The Recruitment Pipeline from Alt-Lite to Alt-Right (Part 1)**

https://medium.com/@notcolloquial/a-network-analysis-of-white-nationalism-the-recruitment-pipeline-from-alt-lite-to-alt-right-part-f9959ce1162b


**List of figures**

*From Alt Right to Alt Lite: Naming the Hate*

https://www.adl.org/education/resources/backgrounders/from-alt-right-to-alt-lite-naming-the-hate

*Who's who - Hope not hate*

https://alternativeright.hopenothate.com/whos-who

# Ideas

## Twitter

Get the timeline of Alt Righters and then everyone who follows them. Then get their timelines as well.

# Hate Speech Data

## Data Sets

** R package for datasets**

https://github.com/jimtyhurst/hate_speech_detection_for_twitter

Zeerak Waseem and Dirk Hovy: Hateful Symbols or Hateful People? Predictive Features for Hate Speech Detection on Twitter. NAACL SRW, 2016. [Data](https://github.com/zeerakw/hatespeech)

Zeerak Waseem: Are You a Racist or Am I Seeing Things? Annotator Influence on Hate Speech Detection on Twitter. NLP and Computational Social Science, 2016. [Data](https://github.com/zeerakw/hatespeech)

Davidson, Thomas, et al. "Automated Hate Speech Detection and the Problem of Offensive Language." arXiv preprint arXiv:1703.04009 (2017). [Data](https://github.com/t-davidson/hate-speech-and-offensive-language)

--------------------------------------------------------------------------------------

Racism and Sexism labelled data
https://github.com/ninkle/hate-speech-detection

Ellery Wulczyn, Nithum Thain, Lucas Dixon: Ex Machina: Personal Attacks Seen at Scale, 2016. [Data](https://figshare.com/articles/Wikipedia_Detox_Data/4054689)
 
Björn Ross, Michael Rist, Guillermo Carbonell, Ben Cabrera, Nils Kurowsky, Michael Wojatzki: Measuring the Reliability of Hate Speech Annotations: The Case of the European Refugee Crisis. In Proceedings of NLP4CMC III: 3rd Workshop on Natural Language Processing for Computer-Mediated Communication, Bochum, September 2016, pp. 6-9. [Data](https://github.com/UCSM-DUE/IWG_hatespeech_public?files=1)
 




## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
