---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
tibble::tribble(
                                  ~X,          ~Location, ~Min, ~Max,
                    "Partly cloudy.",         "Brisbane",   19L,   29L,
                    "Partly cloudy.", "Brisbane Airport",   18L,   27L,
                  "Possible shower.",       "Beaudesert",   15L,   30L,
                    "Partly cloudy.",        "Chermside",   17L,   29L,
    "Shower or two. Possible storm.",           "Gatton",   15L,   32L,
                  "Possible shower.",          "Ipswich",   15L,   30L,
                    "Partly cloudy.",    "Logan Central",   18L,   29L,
                     "Mostly sunny.",            "Manly",   20L,   26L,
                    "Partly cloudy.",    "Mount Gravatt",   17L,   28L,
                  "Possible shower.",            "Oxley",   17L,   30L,
                    "Partly cloudy.",        "Redcliffe",   19L,   27L
    )
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
