
%<!-- Titleseite -->
\thispagestyle{empty}
\begin{titlepage}
\BgThispage
\newgeometry{left=1cm,right=4cm}
\vspace*{2cm}
\noindent
\textcolor{white}{\bigsf Tracking the Alt Right}

\begin{addmargin}[1em]{0em}
\textcolor{white}{\bigsub Using Machine Learning to Track Alt Right Commentary on Social Media}
\end{addmargin}

\vspace*{2cm}\par
\noindent
\begin{addmargin}[3em]{0em}
{\bignice Coding Guidelines}
\end{addmargin}

\vspace*{1cm}\par
\begin{minipage}{0.35\linewidth}
    \begin{flushright}
        \printauthor
    \end{flushright}
\end{minipage} \hspace{15pt}
%
\begin{minipage}{0.02\linewidth}
    \rule{1pt}{210pt}
\end{minipage} \hspace{-10pt}
%
\begin{minipage}{0.66\linewidth}
\vspace{5pt}
\begin{addmargin}[3em]{0em}
\textbf{Project Goal:}
The goal of this project is to track the Alt Right on various Social Media platforms (Facebook, Twitter and YouTube). We seek to identify their content, talking points and narratives by applying machine learning algorithms and natural language processing such as sentiment analysis and topic modeling. In order to do this we accumulated a data set of \textit{over 15 Million comments and tweets posted online during the entire year of 2017} from Social Media accounts that are associated with the Alt Right. 

\vspace{5pt}

Ultimately, we hope to make this data set publicly available (in an anonymized form), so that other researchers might be able to pursue their own research questions.
Interesting research questions might include: How did the Alt Right react to the Charlottesville rally in August 2017? How do they react to jihadist and/or right-wing extremist terror attacks? In which ways does the Alt Right differ from the Alt Light? What talking points do they share? 

\vspace{5pt}

The findings of this project will be presented at a \href{http://www.voxpol.eu/vox-pol-workshop-countering-violent-extremism-online-impact-civil-liberties/}{Voxpol Online-Extremism workshop at the University of Oxford}.
\end{addmargin}
\end{minipage}
\end{titlepage}
\restoregeometry

\clearpage
\tableofcontents

\newpage



%\clearpage
%
%%<!-- Inhaltsverzeichnisse -->
%\thispagestyle{empty}
%\setstretch{1.15}
%\tableofcontents
%\listoffigures
%
%\clearpage
%\setstretch{1.44}
%<!-- \onehalfspacing -->